Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-21 journal/article.tex
S: Piloting

The agile model was usually tried out in the organization before rolling it out
on a general level. Having a pilot project was reported as a significant success
factor in several cases [P3, P9, P38].
The pilot project gave proof that the agile model would be suitable for the
organization and the general acceptance of agile was increased [P3, 17].
The pilot also cleared disbeliefs of the suitability of agile for large
organizations, and created acceptance for both development and management [P31,
P36].

@@

>>>>

The agile model was usually tried out in the organization before rolling it out
on a general level. Having a pilot project was reported as a significant success
factor in several cases [P3, P9, P38].
The pilot project gave proof that the agile model would be suitable for the
organization and the general acceptance of agile was increased [P3, 17].
The pilot also cleared disbeliefs of the suitability of agile for large
organizations, and created acceptance for both development and management [P9,
P31, P36].

@@

% Pilot provides information on how to do the rest of the transformation

A particular benefit in piloting was that it provided knowledge on how to fit
the agile method to the particular organization.
A pilot project enabled the organization to get feedback on how teams and
managers are best introduced to the new methods [P8, P22].
Organizations met challenges in the pilot projects. However, the pilot projects
served as valuable learning experiments providing insight in how to mitigate
problems when the rest of the organization is transforming [P27, P40, P45].
